A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2022-04-19 paper_journal_edits.tex
2.2 and 2.3
typos
merge

\begin{definition}
We say that a classical field theory $(E_N, \omega_N, S_N)$ on $N$ is a \defterm{dimensional reduction} along $p$ of the classical field theory $(E_M, \omega_M, S_M)$ on a manifold $M$ if one is given the data of a linear isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
\begin{itemize}
\item The diagram
\[
\xymatrix{
p^* E_N\otimes p^* E_N \ar^{\omega_N}[r] \ar^{\sim}[d] & p^*\Dens_N[-1] \ar^{\sim}[d] \\
E_M\otimes E_M \ar^{\omega_M}[r] & \Dens_M[-1]
}
\]
is commutative.

\item Under the map $p^*\colon \cE_N\rightarrow \cE_M$ we have $p^* S_N = S_M$ in $\oloc(\cE_M)$.
\end{itemize}
\end{definition}

\begin{remark}
The last condition involves a pullback of local functionals. Using the natural embeddings
\[\oloc(\cE_M)\subset \cO(\cE_{M, c}),\qquad \oloc(\cE_N)\subset \cO(\cE_{N, c})\]
we can interpret $S_N$ and $S_M$ as functionals on compactly-supported fields. Under these embeddings the pullback of local functionals corresponds to the map
\[\cO(\cE_{N, c})\longrightarrow \cO(\cE_{M, c})\]
which is the restriction under the map $\cE_{M, c}\rightarrow \cE_{N, c}$ given by integrating fields over the fibers of $p\colon M\rightarrow N$ for which we use the fiberwise density provided by the isomorphism $p^*\Dens_N\cong\Dens_M$; these integrals are convergent due to the compact support condition.
\end{remark}

@@

\begin{prop}
Suppose $Q_1,Q_2$ and $\lambda\in\Gamma(N, \Sigma)$. Then
\[\sd{\d}\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{\d} \lambda) Q_2.\]
\label{prop:cliffordactionproperty2}
\end{prop}

@@

\begin{prop}
Suppose $Q\in\Sigma$ and $X\in\Omega^p(N)$. Then
\[\sd{\d}(\rho(X) Q) = \rho(\d X)Q + (-1)^{n(1+p)}\rho(\ast \d\ast X) Q\]
as sections of $\Sigma^* \to N$. 
\label{prop:cliffordactionproperty3}
\end{prop}

>>>>

\begin{definition}
We say that a classical field theory $(E_N, \omega_N, S_N)$ on $N$ is a \defterm{dimensional reduction} along $p$ of the classical field theory $(E_M, \omega_M, S_M)$ on a manifold $M$ if one is given the data of a linear isomorphism $p^* E_N\cong E_M$ of the bundles of BV fields satisfying the following conditions:
\begin{itemize}
\item The diagram
\[
\xymatrix{
p^* E_N\otimes p^* E_N \ar^{\omega_N}[r] \ar^{\sim}[d] & p^*\Dens_N[-1] \ar^{\sim}[d] \\
E_M\otimes E_M \ar^{\omega_M}[r] & \Dens_M[-1]
}
\]
is commutative.
\item Via the projection map $p \colon M \to N$ we have $p^* S_N = S_M$ in $\oloc(\cE_M)$ (see the remark below).
\end{itemize}
\end{definition}

\begin{remark}
The last condition involves a pullback of local functionals.
Indeed, the isomorphisms $p^* E_N \cong E_M$ and $p^* {\rm Dens}_M \cong {\rm Dens}_N$ determine a map $p^* \colon \oloc(\cE_N) \to \oloc(\cE_M)$ defined as follows. 
First, we define a map
\[
p^* \colon \cO(\cE_{N,c}) \to \cO(\cE_{M,c}) 
\]
as the restriction of the map $\cE_{M, c}\rightarrow \cE_{N, c}$ given by integrating fields over the fibers of $p\colon M\rightarrow N$ which uses the fiberwise density provided by the isomorphism $p^*\Dens_N\cong\Dens_M$---these integrals are convergent due to the compact support condition.
Next, we use the natural embedding
\[\oloc(\cE_M)\subset \cO(\cE_{M, c})
\]
to interpret any local functional $S \in \oloc(\cE_M)$ as a functional on compactly-supported fields $\cE_{M,c}$. 
It is immediate to see that if $S$ is a local functional then so is $p^*S$ and hence we obtained the desired map.
\end{remark}

@@

\begin{prop}
Suppose $Q_1,Q_2$ are covariantly constant sections of $\Sigma$ and $\lambda$ is a general smooth section of $\Sigma$.
Then
\[\sd{\d}\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{\d} \lambda) Q_2\]
\label{prop:cliffordactionproperty2}
as sections of $\Sigma \to N$. 
\end{prop}

@@

\begin{prop}
Suppose $Q$ is a covariantly constant section of $\Sigma$ and $X\in\Omega^p(N)$. Then
\[\sd{\d}(\rho(X) Q) = \rho(\d X)Q + (-1)^{n(1+p)}\rho(\ast \d\ast X) Q\]
as sections of $M = \Sigma \oplus \Sigma^* \to N$. 
\label{prop:cliffordactionproperty3}
\end{prop}
